\chapter*{Preface}
\setheader{Preface}

This thesis project is the culmination of master's degree in applied mathematics at the TU Delft. During my time at the TU's distributed systems group I was able to contribute to the open source and anonymous P2P file sharing network {\it Tribler}, both as a research assistant as well as with the contents of this master's thesis. I am very happy to have been able to apply my mathematical knowledge to a real-life setting in the field of computer science and hope that my contributions made to this field will prove useful to further research conducted at this group. In particular, I'm excited about the possibility of my research advancing the {\it Tribler} P2P file sharing platform which beyond simply facilitating the distribution of digital media, has made big steps in ensuring freedom of communication and information transfer as well as preserving the autonomy of peoples' digital lives under oppressive and authoritarian regimes. As a firm believer in the openness and freedom of the Internet I could not speak more highly of the values and endeavours of the Tribler development team and its head Johan Pouwelse, who along with Dion Gijswijt, has been my daily supervisor in this project. \vspace{1em}\\

\noindent{}I would like to express my deepest gratitude to both of my daily supervisors for their guidance and input throughout this thesis project. Johan Pouwelse for his infectious excitement and motivation delivered on a daily basis as well as his input throughout weekly meetings and brainstorming sessions in which he provided me with many thought-provoking impulses. Dion Gijswijt for the many fruitful meetings in which he helped me futher my work with high precision and sharpness. I would also like to thank Johan for facilitating a research visit at the Sokendai graduate school of advanced studies in Japan, in which I was able to collaborate with Hisashi Ohtsuki and his team of evolutionary biologists and learn about reputation mechanisms in networks of biological organisms. While this research was highly interesting, it unfortunately did not fit into the narrative of this thesis project and is therefore listed in the appendix. I would also like to thank members of the distributed systems group Martijn de Vos, Quinten Stokkink, Can Umut Ileri and Bulat Nasrulin for proofreading my work and their important input during brainstorming sessions. The team created a very pleasant and supportive working environment. The many (many) coffee breaks were always an enjoyable time and the smell of coffee will forever trigger memories of Quinten's charming sarcasm in my mind. I'd also like to thank my two friends Jetse Brouwer and Sacheendra Talluri for the fun times together on the third floor and at the "$/$pub". Lastly, I'd like to thank my family. Their continuous motivation and support has encouraged me to work hard and push through times of discouragement. \vspace{1em}\\



\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Den Haag, April 2020
\makeatother}
\end{flushright}

