\documentclass[whitelogo]{tudelft-report}
\usepackage{float}
\usepackage{natbib}
\usepackage{changes}
%\usepackage{draftwatermark}
%\SetWatermarkScale{1}
%\usepackage{todonotes}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{color,soul}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage[utf8]{inputenc}
\usepackage{latexsym}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[justification=centering]{caption}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}[section]
\theoremstyle{proposition}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{corollary}
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{lemma}
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{example}
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[section]

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\begin{document}
%% Use Roman numerals for the page numbers of the title pages and table of
%% contents.
\frontmatter

%% Uncomment following 19 lines for a cover with a picture on the lower half only
%\title[tudelft-white]{Title}
%\subtitle[tudelft-cyan]{Optional subtitle}
%\author[tudelft-white]{J.\ Random Author}
%\affiliation{Technische Universiteit Delft}
%\coverimage{cover.jpg}
%\titleoffsetx{10cm}
%\titleoffsety{10cm}
%\afiloffsetx{1cm}
%\afiloffsety{18cm}
%\covertext[tudelft-white]{
%    \textbf{Cover Text} \\
%    possibly \\
%    spanning 
%    multiple 
%    lines
%    \vfill
%    ISBN 000-00-0000-000-0
%}
%\makecover

%% Uncomment following 16 lines for a cover with a picture on the lower half only
\title[tudelft-white]{{\fontsize{45}{49}\selectfont On the \vspace{0.1em}\\ Sybil-Proofness of Accounting Mechanisms in P2P\vspace{0.2em}\\ Networks}}%{{\HUGE \textbf{Sybil-Proof Accounting Mechanisms in P2P Networks}}}
% \subtitle[tudelft-black]{Optional subtitle}
\author[tudelft-white]{Alexander\ Stannat}
\affiliation{Delft University of Technology}
%\coverimage{tank.jpg}
%\covertext[tudelft-white]{
%    \textbf{Cover Text} \\
%    possibly \\
%    spanning 
%    multiple 
%    lines
%    \vfill
%    ISBN 000-00-0000-000-0
%}
%\setpagecolor{tudelft-cyan}
\makecover[split]


%% Include an optional title page.
\input{title}
\input{abstract}
\input{preface}

\tableofcontents

%% Use Arabic numerals for the page numbers of the chapters.
\mainmatter
\input{introduction}

\input{mathematical_framework}

\input{sybil_gain}

\input{representativeness}

\input{impossibility_results}

\input{sybil_proofness}

%\input{physical_proximity}

\input{conclusion}

%% Use letters for the chapter numbers of the appendices.
\appendix

\input{appendix}

\bibliography{report}
\begin{thebibliography}{9}
\bibitem{Ranking Systems: The PageRank Axioms}
Altman, Alon, and Moshe Tennenholtz. "Ranking systems: the PageRank axioms." Proceedings of the 6th ACM conference on Electronic commerce. ACM, 2005.
\bibitem{Big Data Meets Big Brother as China Moves to Rate its Citizens}
Botsman, Rachel. "Big data meets Big Brother as China moves to rate its citizens." Wired UK 21 (2017).
\bibitem{An Optimal Strategy to Solve the Prisoner's Dilemma}
Bravetti, Alessandro, and Pablo Padilla. "An optimal strategy to solve the Prisoner’s Dilemma." Scientific reports 8.1 (2018): 1948.
\bibitem{Jetse Thesis}
Brouwer, Jetse. "Consensus-less Security: A truly scalable distributed ledger." Master Thesis. TU Delft 2020. TU Delft Education Repository. Web. Accessed 18.02.2020.
\bibitem{NetFlow}
Buechler, Matthew, et al. Decentralized reputation system for transaction networks. Technical report, University of Pennsylvania, 2015.
\bibitem{Incentives build robustness in BitTorrent}
Cohen, Bram. "Incentives build robustness in BitTorrent." Workshop on Economics of Peer-to-Peer systems. Vol. 6. 2003.
\bibitem{Game Theory}
Ferguson, T.S. "Game Theory, Second Edition" (Mathematics Department UCLA, 2014)
\bibitem{Creating Trust through Verification of Interaction Records}
Harms, Jan-Gerrit. "Creating trust through verification of interaction records." (2018).
\bibitem{Bittorrent is an auction}
Levin, Dave, et al. "Bittorrent is an auction: analyzing and improving bittorrent's incentives." ACM SIGCOMM Computer Communication Review 38.4 (2008): 243-254.
\bibitem{A Survey of Peer-to-Peer Network Security Issues}
Li, James. "A Survey of Peer-to-Peer Network Security Issues." Retrieved November 29 (2007): 2010.
\bibitem{Personalised Hitting Time}
Liu, Brandon K., David C. Parkes, and Sven Seuken. "Personalized hitting time for informative trust mechanisms despite sybils." Proceedings of the 2016 International Conference on Autonomous Agents \& Multiagent Systems. International Foundation for Autonomous Agents and Multiagent Systems, 2016.
\bibitem{Bartercast: A Practical Approach to Prevent Lazy Freeriding in P2P Networks}
Meulpolder, Michel, et al. "Bartercast: A practical approach to prevent lazy freeriding in p2p networks." 2009 IEEE International Symposium on Parallel \& Distributed Processing. IEEE, 2009.
\bibitem{Bitcoin}
Nakamoto, Satoshi. Bitcoin: A peer-to-peer electronic cash system. Manubot, 2019.
\bibitem{Minimum-cut Community Detection}
Newman, Mark EJ. "Detecting community structure in networks." The European Physical Journal B 38.2 (2004): 321-330.
\bibitem{5 Rules for the Evolution of Cooperation}
Nowak, Martin A. "Five rules for the evolution of cooperation." science 314.5805 (2006): 1560-1563.
\bibitem{A Simple Rule for the Evolution of Cooperation on Graphs and Social Networks}
Ohtsuki, Hisashi, et al. "A simple rule for the evolution of cooperation on graphs and social networks." Nature 441.7092 (2006): 502.
\bibitem{How Should we Define Goodness}
Ohtsuki, Hisashi, and Yoh Iwasa. "How should we define goodness?—reputation dynamics in indirect reciprocity." Journal of theoretical biology 231.1 (2004): 107-120.
\bibitem{The leading eight: Social norms that can maintain cooperation by indirect reciprocity}
Ohtsuki, Hisashi, and Yoh Iwasa. "The leading eight: social norms that can maintain cooperation by indirect reciprocity." Journal of theoretical biology 239.4 (2006): 435-444.
\bibitem{Sybil-resistant Trust Mechanisms in Distributed Systems}
Otte, P. "Sybil-resistant trust mechanisms in distributed systems." (2016).
\bibitem{TrustChain: A Sybil-resistant scalable blockchain}
Otte, Pim, Martijn de Vos, and Johan Pouwelse. "TrustChain: A Sybil-resistant scalable blockchain." Future Generation Computer Systems (2017).
\bibitem{Tribler}
Pouwelse, Johan A., et al. "TRIBLER: a social‐based peer‐to‐peer system." Concurrency and computation: Practice and experience 20.2 (2008): 127-138.
\bibitem{PageRank}
Page, Lawrence, et al. The PageRank citation ranking: Bringing order to the web. Stanford InfoLab, 1999. 
\bibitem{On the Sybil-Proofness of Accounting Mechanisms}
Seuken, Sven, and David C. Parkes. "On the Sybil-proofness of accounting mechanisms." (2011).
\bibitem{Accounting Mechanisms for Distributed Work Systems}
Seuken, Sven, Jie Tang, and David C. Parkes. "Accounting mechanisms for distributed work systems." Twenty-Fourth AAAI Conference on Artificial Intelligence. 2010.
\bibitem{Work Accounting Mechanisms: Theory and Practice}
Seuken, Sven, et al. "Work accounting mechanisms: Theory and practice." Working Paper. Department of Informatics. University of Zurich, 2014.
\bibitem{Sybil-proof Accounting Mechanisms with Transitive Trust}
Seuken, Sven, and David C. Parkes. "Sybil-proof accounting mechanisms with transitive trust." Proceedings of the International Foundation for Autonomous Agents and Multiagent Systems (2014).
\bibitem{Cryptography made simple}
Smart, Nigel P. Cryptography made simple. Vol. 481. Cham: Springer, 2016.
\bibitem{A Random Walk Based Trust Ranking in Distributed Systems}
Stannat, Alexander, and Johan Pouwelse. "A Random Walk based Trust Ranking in Distributed Systems." arXiv preprint arXiv:1903.05900 (2019).
\bibitem{Hybrid Transitive Trust Mechanisms}
Tang, Jie, Sven Seuken, and David C. Parkes. "Hybrid transitive trust mechanisms." Proceedings of the 9th International Conference on Autonomous Agents and Multiagent Systems: volume 1-Volume 1. International Foundation for Autonomous Agents and Multiagent Systems, 2010.
\bibitem{Distributed systems: principles and paradigms}
Tanenbaum, Andrew S., and Maarten Van Steen. Distributed systems: principles and paradigms. Prentice-Hall, 2007.
\bibitem{Trust in Distributed Systems}
van den Heuvel, Bram, and Dai, Yinghao. "Trust in Distributed Systems." (2019).  


\bibitem{The Early Days of Mass Internet Piracy Were Awesome Yet Awful}
andy@torrentfreak.com "The Early Days of Mass Internet Piracy Were Awesome Yet Awful". \texttt{https://torrentfreak.com/the-early-days-of-mass-internet-piracy-were-awesome- \\ yet-awful-180211/} (11.02.2018)

\bibitem{Prisoner's Dilemma Image}
PsychologyProf@gmail.com "Game Theory -- best strategy for Prisoner's Dilemma used in advice column for real life situation" \texttt{http://cogsciandtheworld.blogspot.com/2009/10/game-theory-best- \\ strategy-for-prisoners.html} (11.10.2009) 


\end{thebibliography}

\end{document}

